Arrows for Parallel Computation

### 2018-01-07 paper/content/benchmarks.tex
every section has text now

The preceding section has shown that PArrows are expressive. This section evaluates the performance overhead of this compositional abstraction in comparison to  GpH and the |Par| Monad on shared memory architectures and Eden on  a distributed memory cluster.
We start by explaining the hardware and software stack and outline the benchmark programs, and motivations for choosing them. Before we go into detail on the benchmarks we
also shortly address hyper-threading and why we do not use it in our
benchmarks. Our results show that PArrows hold up in terms of performance when compared to the original parallel Haskells, starting with the shared-memory variants (GpH, |Par| Monad and Eden~CP) and concluding with Eden in a distributed memory setting.

@@

\subsection{Measurement Platform}

>>>>

The preceding section has shown that PArrows are expressive. This section evaluates the performance overhead of this compositional abstraction in comparison to  GpH and the |Par| Monad on shared memory architectures and Eden on  a distributed memory cluster.
We describe our measurement platform, the benchmark results -- the shared-memory variants (GpH, |Par| Monad and Eden~CP) followed by Eden in a distributed memory setting, and conclude that PArrows hold up in terms of performance when compared to the original parallel Haskells.

@@

\subsection{Measurement Platform}
We start by explaining the hardware and software stack and outline the benchmark programs and motivation for choosing them. We also shortly address hyper-threading and why we do not use it in our benchmarks.
